Topic 21 Experiment and analysis

### 2018-05-17 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Almost finished the May 2018 TeX file

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis

  \end{itemize}
}
\end{frame}

@@

\begin{frame}{On going work}
  A series of works are still on-going \textcolor{ta3scarletred}{or
    yet to be started}
  \begin{itemize}[<+->]
    \item Neutral density estimate from light emission
      \textbf{M. Agostini}
    \item Wall embedded probe analysis \textbf{S. Costea,
        M. Spolaore}
    \item Shoulder from Reflectometry analysis \textbf{E. Sieglun}
    \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
      along flux tube and compare to measurement}
    \item \textcolor{ta3scarletred}{Balmer series analysis for
        recombination analysis on TCV \textbf{K. Verhaegh}}
  \item \textcolor{ta3scarletred}{HFSD}
    \item \textcolor{ta3scarletred}{\ldots}

>>>>

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis
  \end{itemize}
}
\only<3>{
  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
  \begin{itemize}
    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
    \item $\tau_b$ estimated from FWHM of Conditional Avearage
      (\alert{different from Carralero}) including asymmetric part
      (\alert{different from Tsui})
  \end{itemize}
}
\only<4>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
  \includegraphics[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCorrelation}
    \end{column}
    \begin{column}{0.5\textwidth}
  \begin{itemize}
    \item Correlation on TCV computed using a gaussian Fit of the
      central part (better resolution)
    \item on AUG the correlation is in general asymmetric. Maximum
      time lag estimated from the zeros of the imaginary part of the
      hilbert transform of the correlation function
  \end{itemize}
    \end{column}
  \end{columns}
}

@@

\begin{frame}{On going work}
  A series of works are still on-going \textcolor{ta3scarletred}{or
    yet to be started}
  \begin{itemize}[<+->]
    \item Neutral density estimate from light emission
      \textbf{M. Agostini}
    \item Wall embedded probe analysis \textbf{S. Costea,
        M. Spolaore}
    \item Shoulder from Reflectometry analysis \textbf{E. Sieglun}
    \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
      along flux tube and compare to measurement}
    \item \textcolor{ta3scarletred}{Balmer series analysis for
        recombination analysis on TCV \textbf{K. Verhaegh}}
    \item \textcolor{ta3orange}{GPI analysis and comparison with probe
      \textbf{Walkden, Cziegler}}  
  \item \textcolor{ta3scarletred}{HFSD}
    \item \textcolor{ta3scarletred}{\ldots}
